---
title: "Untitled"

date:  "`r Sys.Date()`"

output:
  imbiReport2::imbi_report_tex:
    toc: true
    number_sections: true
    toc_depth: 4
    df_print: kable
  imbiReport2::imbi_report_word:
    toc: true
    toc_depth: 4
    df_print: kable
  imbiReport2::imbi_report_html:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
    
biometrician: |
  | Joe Doe
  | joe.doe@somewhere.online
    
contacts: |
  | Joe Doe
  | joe.doe@somewhere.online
  | 
  | Joe Doe
  | joe.doe@somewhere.online

data-source: |
  | Where did you get it from
  
data-supplier: |
  | Who gave it to you?
  
data-date: |  
  | When did you get it?
 
abstract: > 
  This is an example abstract. It briefly describes what this study is about. This study is about examples. A lot can be learned from examples. This text is so long, because it is supposed to fill 2 rows.
  
draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE
)
```

```{r dependencies, include=FALSE}
library(tidyverse)
library(DescrTab2)
```

# Introduction
Short introduction to the background of the trial (as described in the study protocol).


# Objective of the trial
Short and clear description of the trial objectives (as described in the study protocol).

# Study design
As described in the study protocol.

# Treatment
Experimental group:


Control group: 


# Aims of the trial
Primary endpoint


Secondary endpoints


# Analysis sets
Description of the analysis sets (e.g. intention-to-treat, per protocol, safety population).

# Data handling
Methods for handling withdrawals, protocol deviations, missing values, and outliers.


Missing values


# Handling of unresolved data issues
Handling of unresolved data inssues

# Statistical methods
## Demographics and baseline characteristics
Both treatment groups were characterized using descriptive methods based on the FAS and PP set. A flowchart is given to illustrate patient numbers included in the different analysis sets. Deviations from the inclusion and exclusion criteria were listed individually.

## Primary endpoint
Clearly described hypotheses and statistical methods for each primary endpoint including covariates (baseline value of the parameter of interest, other covariates such as study center) and their rationale used for adjustment (programming statements may be given), methods to verify the assumptions of the statistical model and description of the methods used if assumptions are not fulfilled. Describe handling of multiple comparisons if applicable.

### Interim analysis
Describe interim analyses if applicable.

### Sensitivity analyses for the primary endpoint
Describe sensitivity analyses

## Secondary endpoints
Clearly described statistical methods for each secondary endpoint including covariates and their rationale used for adjustment, methods to verify the assumptions of the statistical model and description of the methods used if assumptions are not fulfilled
All secondary endpoints were analyzed based on the FAS and the PP set. In case of categorical variables, p-values correspond to the Chi-squared test, in case of continuous variables, p-values are given for the non-parametric U-test.

## Safety
Clearly described statistical methods for safety analyses.

## Differences to trial protocol specified in the SAP
Description and explanation of differences to the trial protocol

## Analyses not preprespecified, more detailed specifications and differences to the SAP.
Analyses not preprespecified

## Interpretation of results
Interpretation regarding the primary endpoint, limitations of the interpretation.

## Software
This analysis was performed using R version `r paste0(R.Version()$major, ".",  R.Version()$minor)`

# Results
## Flow chart of enrolled patients
Flow chart

## Inclusion/exclusion criteria
Inclusion exclusion

## Demographics and baseline characteristics
Demo

### Full analysis set
FAS

## Primary endpoint
Primary

## Secondary endpoints
Secondary

## Safety
AEs

## Applied study medication
Meds

## Study termination
Term

##	Other analyses

#	References
Ref

# Listings
## 	Discontinued patients
Disc

## 	Protocol deviations
Deviations

##	Patients excluded from the efficacy analysis
Excluded

##	Demographic data
Demolisting

##	Compliance and/or drug concentration data
Compliance

##	Individual response data
Responses

##	Adverse events
AEs

# Appendix

## Original R output
orig

## Data issues
issues

## Session Information

```{r session-info, echo=FALSE} 
sessionInfo()
```
