---
title: "Usage guidance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = identical(Sys.getenv("NOT_CRAN"), "true")
)
```

```{r setup}
library(OptimalGoldstandardDesigns)
```

# Introduction
This package assumes that a hierarchical testing procedure
for the three-arm gold-standard non-inferiority design is applied.
The first test aims to establish assay sensitivity of the trial. It is a test of
superiority of the experimental treatment (T) against the placebo treatment (P).
If assay sensitivity is successfully established, the treatment is tested
for non-inferiority against the control treatment (C).
Individual observations are assumed to be normally distributed, where higher values
correspond to better treatment effects. Testing is assumed to be done via
Z test statistics.

We highly recommend reading our open-access article
[(Meis et al., 2022)](https://doi.org/10.1002/sim.9630)
where the theoretical background of this package is explained.

# Some examples from the paper
To showcase the capabilities of this package, we will reproduce some results
from the paper in the following.

It should be noted that the results will not completely agree with the
results from the paper, as the calculations in the paper used much
lower error tolerances and more function evaluations.

To achieve results closer to the results from the paper, you can
supply the following options, though this will significantly increase
computation times:

```{r, eval=FALSE}
  mvnorm_algorithm = mvtnorm::Miwa(
    # steps = 128,
    steps = 4097,
    checkCorr = FALSE,
    maxval = 1000),
  nloptr_opts = list(algorithm = "NLOPT_LN_SBPLX",
                     # xtol_abs = 1e-3,
                     # xtol_rel = 1e-2,
                     # maxeval = 2000,
                     xtol_abs = 1e-10,
                     xtol_rel = 1e-9,
                     maxeval = 2000,
                     print_level = 0)
```

You may also want to put 

```{r, eval=FALSE}
print_progress = TRUE
```

when running code interactively to see the progress of the optimization.

## Design from Table 2
The designs from in Table 2 from the paper are optimized to minimize the
expected sample size under the alternative hypothesis.

### Design 1, $\beta = 0.2$
This is (approximately) the first line in Table 2 from the paper:
```{r}
tab1_D1 <- optimize_design_onestage(
  alpha = .025,
  beta = .2,
  alternative_TP = .4,
  alternative_TC = 0,
  Delta = .2,
  print_progress = FALSE
)
tab1_D1
```

### Design 2, $\beta = 0.2$
This is (approximately) the second line in Table 2 from the paper:

```{r}
optimize_design_twostage(
  cP1 = tab1_D1$stagec[[1]]$P, # The allocation ratios are enforced to be
  cC1 = tab1_D1$stagec[[1]]$C, # the same as in the optimal single-stage design.
  cT2 = 1,          
  cP2 = tab1_D1$stagec[[1]]$P, 
  cC2 = tab1_D1$stagec[[1]]$C, 
  
  bTP1f = -Inf,     # These two boundary conditions enforce no futility stops.
  bTC1f = -Inf,
  
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE
)
```

### Design 3, $\beta = 0.2$
This is (approximately) the third line in Table 2 from the paper:

```{r}
optimize_design_twostage(
  bTP1f = -Inf,     # These two boundary conditions enforce no futility stops.
  bTC1f = -Inf,
  
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE
)
```

### Design 4, $\beta = 0.2$
This is (approximately) the fourth line in Table 2 from the paper:

```{r}
optimize_design_twostage(
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE,
  binding_futility = FALSE
)
```

### Design 5, $\beta = 0.2$
This is (approximately) the fourth line in Table 2 from the paper:

```{r}
optimize_design_twostage(
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE,
  binding_futility = TRUE
)
```


## Design from Table 3
Next, we will optimize a design under a combination of null and alternative
hypothesis.

### Design 5, $\beta = 0.2$, $\lambda = 0.9$
This is (approximately) the third line in Table 3 from the paper:

```{r}
optimize_design_twostage(
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE,
  binding_futility = TRUE,
  lambda = 0.9
)
```

## Design from Table 4
Now we will optimize a design under the alternative while putting an
extra penalty on placebo group sample size.

### Design 5, $\beta = 0.2$, $\kappa = 0.5$
This is (approximately) the fourth line in Table 2 from the paper:

```{r}
optimize_design_twostage(
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE,
  binding_futility = TRUE,
  kappa = 0.5
)
```

## Design from Table 5
Next, we will optimize a design under a combination of null and
alternative hypothesis while including a penalty on the placebo group
sample size.

### Design 5, $\beta = 0.2$, $\lambda = 0.9$, $\kappa = 1$
This is (approximately) the seventh line in Table 2 from the paper:

```{r}
optimize_design_twostage(
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE,
  binding_futility = TRUE,
  lambda = .9,
  kappa = 1 
)
```


## Other options
### Penalizing the maximum sample size
```{r}
optimize_design_twostage(
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE,
  eta = 1
)
```

### Optimizing between group allocation with enforced between stage allocation at 1
```{r}
optimize_design_twostage(
  cT2 = 1,           # These three boundary conditions enforce a
  cP2 = quote(cP1),  # between-stage allocation ratio of one.
  cC2 = quote(cC1),  # The quote() command is necessary for this to work.
  
  bTP1f = -Inf,      # These two boundary conditions enforce no futility stops.
  bTC1f = -Inf,
  
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE
)
```

### Using a custom objective function
You can replace the default objective function by any quoted expression.
In the following example, we optimize the design parameters to minimize
the expected squared sample size under the alternative hypothesis.
These expressions can make use of internal objects created in the
objective evaluation methods, check out the source code of
`optimize_design_twostage` in the `optimization_methods.R` file for more
information. `ASN`, `ASNP`, `n` and `final_state_probs` could be useful object
for crafting a custom objective function.

```{r}
optimize_design_twostage(
  beta = 0.2,
  alternative_TP = 0.4,
  alternative_TC = 0,
  Delta = 0.2,
  print_progress = FALSE,
  objective = quote((final_state_probs[["H1"]][["TP1E_TC1E"]] + final_state_probs[["H1"]][["TP1F_TC1F"]]) *
                      (n[[1]][["T"]] + n[[1]][["P"]] + n[[1]][["C"]])^2 +
                      (final_state_probs[["H1"]][["TP1E_TC12E"]] + final_state_probs[["H1"]][["TP1E_TC12F"]]) *
                      (n[[1]][["T"]] + n[[1]][["P"]] + n[[1]][["C"]] + n[[2]][["T"]] + n[[2]][["C"]])^2 +
                      (final_state_probs[["H1"]][["TP12F_TC1"]] + final_state_probs[["H1"]][["TP12E_TC12E"]] +
                         final_state_probs[["H1"]][["TP12E_TC12F"]]) *
                      (n[[1]][["T"]] + n[[1]][["P"]] + n[[1]][["C"]] + n[[2]][["T"]] + n[[2]][["P"]] + n[[2]][["C"]])^2)
)
```

# References
Meis, J, Pilz, M, Herrmann, C, Bokelmann, B, Rauch, G, Kieser, M. Optimization of the two-stage group
sequential three-arm gold-standard design for non-inferiority trials. *Statistics in Medicine.* 2023; 42(
4): 536– 558. [doi:10.1002/sim.9630](https://doi.org/10.1002/sim.9630).

