---
title: "Mathematical details"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mathematical_details}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(OptimalGoldstandardDesigns)
```

The version of the three arm gold-standard non-inferiority design used in this package assumes a
hierarchical testing procedure is applied.
The first test aims to establish assay sensitivity of the trial. It is a test of
superiority of the experimental treatment (T) against the placebo treatment (P).
If assay sensitivity is successfully established, the treatment is tested for non-inferiority
to the control treatment (C).

Individual observations are assumed to be normally distributed, where higher values
correspond to better treatment effects. We denote the test statistics for the
two hypothesis by Z_TP1 and Z_TC1, where Z_TC1 already incorporates
the non-inferiority margin \eqn{\Delta}. The respective critical values are given by
bTP1e, bTC1e, bTP2e and bTC2e. (The optimizer searches for the optimal values of bTP1e and
bTC1e, while bTP2e and bTC2e are implicitly defined.)
